### 2024-08-19 ms.qmd
updates

```{r, packages}
#| label: packages
pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes, forcats, MASS,
fitdistrplus)
```

@@

```{r, models}
#| label: models
# Fitting the model and extraction of posteriors 
refit = FALSE
if(refit){
  # Get the formula and family of variables
  lat <- bf(latency ~ test_type*temp*cort + sex + age + (1|lizard_id) + (1|clutch), family = negbinomial())
  choice <- bf(choice ~ test_type*temp*cort + sex + age + (1|lizard_id) + (1|clutch), family = bernoulli(link = "logit"))
  int <- bf(compared_interest ~ test_type*temp*cort + sex + age + (1|lizard_id) + (1|clutch),
    family = student())
  # Fit the model
  model <- brm(lat + choice + int,
                chains = 4, cores = 4, iter = 3000, warmup = 1000, control = list(adapt_delta = 0.99),
                data = data_num)
    # Write the model to a file
    saveRDS(model, file = here("output/models/model_num.rds"))
  } else {
      # Read the model from a file
      model <- readRDS(file = here("output/models/model_num.rds"))
  } 
  # Extract posteriors
posteriors <- as_draws_df(model)
```

```{r, resultsorg}
#| label: resultsorg
# Organise the estimated results based on the posteriors
##
#
# If I want to get the probability of choosing right per treatment and trial from the posteriors, I will need to take Intercept of each ch treatment and add it, then get the trial-treatment slope, and then model each probability as:
# P = exp(intercept + slope*trial) / (1 + exp(intercept + slope*trial))
# And to estimate the Latency it will have to be the same but
# Lat = intercept * exp(slope*trial)
# What is trial here?
# What should I do to get the estimated compared_interest if it follows a t student distribution?
# Would be:
# Estimated interest = intercept + slope * trial 
# correct?
# How do I get each Intercept for each treatment/trial? And the slope?
# 
# E.g.: Getting estimated Latency for CORT-Hot in the 1 VS 3 trial (base level is CORT-Cold test 1 VS 4)
# Intercept = posteriors$b_latency_Intercept + posteriors$b_latency_test_type1VS3 + posteriors$b_latency_tempHot 
# Slope = b_latency_test_type1VS3:tempHot
# Estimated Latency = Intercept * exp(Slope * Trial?)
# 
```

@@

#### Checking the models plots  
```{r, checking_model, out.width="70%", fig.align="center"}
# Chunk for plotting the model
#
plot(model)
```

>>>>

```{r, packages}
#| label: packages
pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest, broom, tidybayes, forcats, MASS,
fitdistrplus, DHARMa)
```

@@

```{r, models}
#| label: models
# Fitting the model and extraction of posteriors 
refit = FALSE
if(refit){
  # Get the formula and family of variables
  lat <- bf(log(latency) ~ test_type*temp*cort + sex + age + (1|lizard_id) + (1|clutch), family = gaussian())
  choice <- bf(choice ~ test_type*temp*cort + sex + age + (1|lizard_id) + (1|clutch), family = bernoulli(link = "logit"))
  int <- bf(compared_interest ~ test_type*temp*cort + sex + age + (1|lizard_id) + (1|clutch),
    family = gaussian())
  # Fit the model
  model <- brm(lat + choice + int,
                chains = 4, cores = 4, iter = 3000, warmup = 1000, control = list(adapt_delta = 0.99, max_treedepth =12),
                data = data_num)
    # Write the model to a file
    saveRDS(model, file = here("output/models/model_num.rds"))
  } else {
      # Read the model from a file
      model <- readRDS(file = here("output/models/model_num.rds"))
  } 
# Extract posteriors
posteriors <- as_draws_df(model)
```

```{r, resultsorg}
#| label: resultsorg
# Get predictions for every test and treatment based on the posteriors of the model. We used the function org_post (see func.R) to get the predictions.
source(here("R", "func.R"))
## A) Get predictions
post_lat <- org_post("lat")
post_choice <- org_post("choice")
post_int <- org_post("int")
#
write.csv(post_lat, here("output/Checking/post_lat.csv"))
# 
```

@@

#### Checking the models plots  
```{r, checking_model, out.width="70%", fig.align="center"}
# Chunk for plotting the model
## Initial plot
plot(model)
#
## pp_checks
pp_check(model, resp = "loglatency")
pp_check(model, resp = "choice")
pp_check(model, resp = "comparedinterest")
```
